COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging

### 2021-03-23 paper_files/figure-latex/genderhist-1.tex
replication files

% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:37
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,560.96) --
	(371.71,560.96);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,580.31) --
	(371.71,580.31);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,599.67) --
	(371.71,599.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,619.02) --
	(371.71,619.02);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,570.64) --
	(371.71,570.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,589.99) --
	(371.71,589.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,609.34) --
	(371.71,609.34);

@@

\path[fill=fillColor] (171.81,551.28) rectangle (185.29,565.53);

\path[fill=fillColor] (261.65,551.28) rectangle (275.13,552.76);

\path[fill=fillColor] (216.73,551.28) rectangle (230.21,552.68);

\path[fill=fillColor] (306.57,551.28) rectangle (320.05,560.26);

\path[fill=fillColor] (351.49,551.28) rectangle (364.97,552.60);

\path[fill=fillColor] ( 81.97,551.28) rectangle ( 95.45,591.23);

\path[fill=fillColor] (126.89,551.28) rectangle (140.37,561.27);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,551.28) rectangle (171.81,566.46);

\path[fill=fillColor] (248.18,551.28) rectangle (261.65,552.83);

\path[fill=fillColor] (203.26,551.28) rectangle (216.73,551.98);

\path[fill=fillColor] (293.10,551.28) rectangle (306.57,555.00);

\path[fill=fillColor] (338.02,551.28) rectangle (351.49,551.59);

\path[fill=fillColor] ( 68.50,551.28) rectangle ( 81.97,595.49);

\path[fill=fillColor] (113.42,551.28) rectangle (126.89,562.97);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,551.28) rectangle (158.34,563.83);

\path[fill=fillColor] (234.70,551.28) rectangle (248.18,552.52);

\path[fill=fillColor] (189.78,551.28) rectangle (203.26,554.15);

\path[fill=fillColor] (279.62,551.28) rectangle (293.10,570.72);

\path[fill=fillColor] (324.54,551.28) rectangle (338.02,554.54);

\path[fill=fillColor] ( 55.02,551.28) rectangle ( 68.50,582.79);

\path[fill=fillColor] ( 99.94,551.28) rectangle (113.42,557.86);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,475.33) --
	(371.71,475.33);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,494.68) --
	(371.71,494.68);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,514.04) --
	(371.71,514.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,533.39) --
	(371.71,533.39);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,485.01) --
	(371.71,485.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,504.36) --
	(371.71,504.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,523.71) --
	(371.71,523.71);

@@

\path[fill=fillColor] (171.81,465.65) rectangle (185.29,493.21);

\path[fill=fillColor] (254.91,465.65) rectangle (275.13,465.96);

\path[fill=fillColor] (216.73,465.65) rectangle (230.21,478.12);

\path[fill=fillColor] (306.57,465.65) rectangle (320.05,466.04);

\path[fill=fillColor] (351.49,465.65) rectangle (364.97,467.51);

\path[fill=fillColor] ( 81.97,465.65) rectangle ( 95.45,499.87);

\path[fill=fillColor] (126.89,465.65) rectangle (140.37,466.27);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,465.65) rectangle (171.81,493.68);

\path[fill=fillColor] (234.70,465.65) rectangle (254.91,465.96);

\path[fill=fillColor] (203.26,465.65) rectangle (216.73,478.12);

\path[fill=fillColor] (293.10,465.65) rectangle (306.57,466.04);

\path[fill=fillColor] (338.02,465.65) rectangle (351.49,466.66);

\path[fill=fillColor] ( 68.50,465.65) rectangle ( 81.97,500.26);

\path[fill=fillColor] (113.42,465.65) rectangle (126.89,466.20);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,465.65) rectangle (158.34,480.13);

\path[fill=fillColor] (189.78,465.65) rectangle (203.26,478.66);

\path[fill=fillColor] (279.62,465.65) rectangle (293.10,466.43);

\path[fill=fillColor] (324.54,465.65) rectangle (338.02,489.81);

\path[fill=fillColor] ( 55.02,465.65) rectangle ( 68.50,489.03);

\path[fill=fillColor] ( 99.94,465.65) rectangle (113.42,467.28);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,389.70) --
	(371.71,389.70);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,409.05) --
	(371.71,409.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,428.41) --
	(371.71,428.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,447.76) --
	(371.71,447.76);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,399.38) --
	(371.71,399.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,418.73) --
	(371.71,418.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,438.08) --
	(371.71,438.08);

@@

\path[fill=fillColor] (171.81,380.02) rectangle (185.29,391.63);

\path[fill=fillColor] (254.91,380.02) rectangle (275.13,380.49);

\path[fill=fillColor] (216.73,380.02) rectangle (230.21,380.87);

\path[fill=fillColor] (306.57,380.02) rectangle (320.05,405.72);

\path[fill=fillColor] (351.49,380.02) rectangle (364.97,380.33);

\path[fill=fillColor] ( 81.97,380.02) rectangle ( 95.45,397.83);

\path[fill=fillColor] (126.89,380.02) rectangle (140.37,400.69);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,380.02) rectangle (171.81,391.71);

\path[fill=fillColor] (234.70,380.02) rectangle (254.91,380.56);

\path[fill=fillColor] (203.26,380.02) rectangle (216.73,380.80);

\path[fill=fillColor] (293.10,380.02) rectangle (306.57,404.79);

\path[fill=fillColor] (338.02,380.02) rectangle (351.49,380.10);

\path[fill=fillColor] ( 68.50,380.02) rectangle ( 81.97,398.45);

\path[fill=fillColor] (113.42,380.02) rectangle (126.89,401.23);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,380.02) rectangle (158.34,389.93);

\path[fill=fillColor] (189.78,380.02) rectangle (203.26,382.27);

\path[fill=fillColor] (279.62,380.02) rectangle (293.10,421.21);

\path[fill=fillColor] (324.54,380.02) rectangle (338.02,384.28);

\path[fill=fillColor] ( 55.02,380.02) rectangle ( 68.50,387.84);

\path[fill=fillColor] ( 99.94,380.02) rectangle (113.42,392.10);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,304.07) --
	(371.71,304.07);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,323.42) --
	(371.71,323.42);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,342.78) --
	(371.71,342.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,362.13) --
	(371.71,362.13);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,313.74) --
	(371.71,313.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,333.10) --
	(371.71,333.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,352.45) --
	(371.71,352.45);

@@

\path[fill=fillColor] (171.81,294.39) rectangle (185.29,296.79);

@@

\path[fill=fillColor] (216.73,294.39) rectangle (230.21,295.71);

\path[fill=fillColor] (306.57,294.39) rectangle (320.05,298.88);

\path[fill=fillColor] ( 81.97,294.39) rectangle ( 95.45,363.52);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,294.39) rectangle (171.81,296.71);

@@

\path[fill=fillColor] (203.26,294.39) rectangle (216.73,295.09);

\path[fill=fillColor] (293.10,294.39) rectangle (306.57,295.86);

\path[fill=fillColor] ( 68.50,294.39) rectangle ( 81.97,367.24);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,294.39) rectangle (158.34,297.41);

\path[fill=fillColor] (189.78,294.39) rectangle (203.26,300.20);

\path[fill=fillColor] (279.62,294.39) rectangle (293.10,320.63);

\path[fill=fillColor] ( 55.02,294.39) rectangle ( 68.50,336.74);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,218.44) --
	(371.71,218.44);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,237.79) --
	(371.71,237.79);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,257.14) --
	(371.71,257.14);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,276.50) --
	(371.71,276.50);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,228.11) --
	(371.71,228.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,247.47) --
	(371.71,247.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,266.82) --
	(371.71,266.82);

@@

\path[fill=fillColor] (171.81,208.76) rectangle (185.29,221.77);

\path[fill=fillColor] (261.65,208.76) rectangle (275.13,209.92);

\path[fill=fillColor] (216.73,208.76) rectangle (230.21,212.86);

\path[fill=fillColor] (306.57,208.76) rectangle (320.05,216.97);

\path[fill=fillColor] (351.49,208.76) rectangle (364.97,210.62);

\path[fill=fillColor] ( 81.97,208.76) rectangle ( 95.45,246.00);

\path[fill=fillColor] (126.89,208.76) rectangle (140.37,223.70);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,208.76) rectangle (171.81,221.77);

\path[fill=fillColor] (248.18,208.76) rectangle (261.65,209.92);

\path[fill=fillColor] (203.26,208.76) rectangle (216.73,212.24);

\path[fill=fillColor] (293.10,208.76) rectangle (306.57,214.10);

\path[fill=fillColor] (338.02,208.76) rectangle (351.49,209.69);

\path[fill=fillColor] ( 68.50,208.76) rectangle ( 81.97,248.47);

\path[fill=fillColor] (113.42,208.76) rectangle (126.89,225.48);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,208.76) rectangle (158.34,220.53);

\path[fill=fillColor] (234.70,208.76) rectangle (248.18,210.00);

\path[fill=fillColor] (189.78,208.76) rectangle (203.26,215.50);

\path[fill=fillColor] (279.62,208.76) rectangle (293.10,228.97);

\path[fill=fillColor] (324.54,208.76) rectangle (338.02,216.42);

\path[fill=fillColor] ( 55.02,208.76) rectangle ( 68.50,233.92);

\path[fill=fillColor] ( 99.94,208.76) rectangle (113.42,217.12);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,132.81) --
	(371.71,132.81);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,152.16) --
	(371.71,152.16);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,171.51) --
	(371.71,171.51);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,190.87) --
	(371.71,190.87);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,142.48) --
	(371.71,142.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,161.84) --
	(371.71,161.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,181.19) --
	(371.71,181.19);

@@

\path[fill=fillColor] (171.81,123.13) rectangle (185.29,132.03);

\path[fill=fillColor] (216.73,123.13) rectangle (230.21,124.99);

\path[fill=fillColor] (306.57,123.13) rectangle (320.05,140.08);

@@

\path[fill=fillColor] ( 81.97,123.13) rectangle ( 95.45,149.84);

\path[fill=fillColor] (126.89,123.13) rectangle (140.37,146.12);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,123.13) rectangle (171.81,129.86);

\path[fill=fillColor] (203.26,123.13) rectangle (216.73,124.45);

\path[fill=fillColor] (293.10,123.13) rectangle (306.57,137.53);

\path[fill=fillColor] ( 68.50,123.13) rectangle ( 81.97,152.62);

\path[fill=fillColor] (113.42,123.13) rectangle (126.89,148.68);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,123.13) rectangle (158.34,137.61);

\path[fill=fillColor] (189.78,123.13) rectangle (203.26,126.38);

\path[fill=fillColor] (279.62,123.13) rectangle (293.10,146.59);

\path[fill=fillColor] (324.54,123.13) rectangle (344.75,123.28);

\path[fill=fillColor] ( 55.02,123.13) rectangle ( 68.50,142.72);

\path[fill=fillColor] ( 99.94,123.13) rectangle (113.42,139.62);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,560.96) --
	(717.20,560.96);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,580.31) --
	(717.20,580.31);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,599.67) --
	(717.20,599.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,619.02) --
	(717.20,619.02);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,570.64) --
	(717.20,570.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,589.99) --
	(717.20,589.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,609.34) --
	(717.20,609.34);

@@

\path[fill=fillColor] (517.31,551.28) rectangle (530.78,579.62);

\path[fill=fillColor] (607.15,551.28) rectangle (620.62,552.60);

\path[fill=fillColor] (562.23,551.28) rectangle (575.70,552.68);

\path[fill=fillColor] (696.99,551.28) rectangle (710.46,558.17);

\path[fill=fillColor] (427.47,551.28) rectangle (440.94,581.71);

\path[fill=fillColor] (472.39,551.28) rectangle (485.86,560.26);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (503.83,551.28) rectangle (517.31,579.85);

\path[fill=fillColor] (593.67,551.28) rectangle (607.15,552.60);

\path[fill=fillColor] (548.75,551.28) rectangle (562.23,551.98);

\path[fill=fillColor] (683.51,551.28) rectangle (696.99,556.16);

\path[fill=fillColor] (413.99,551.28) rectangle (427.47,583.33);

\path[fill=fillColor] (458.91,551.28) rectangle (472.39,561.12);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (490.36,551.28) rectangle (503.83,578.77);

\path[fill=fillColor] (580.19,551.28) rectangle (593.67,552.37);

\path[fill=fillColor] (535.27,551.28) rectangle (548.75,555.39);

\path[fill=fillColor] (670.03,551.28) rectangle (683.51,565.84);

\path[fill=fillColor] (400.52,551.28) rectangle (413.99,575.67);

\path[fill=fillColor] (445.44,551.28) rectangle (458.91,557.17);
\definecolor{drawColor}{gray}{0.20}

@@

\path[fill=fillColor] (517.31,465.65) rectangle (530.78,471.85);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:44
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,561.31) --
	(371.71,561.31);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,581.37) --
	(371.71,581.37);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,601.43) --
	(371.71,601.43);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,621.48) --
	(371.71,621.48);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,571.34) --
	(371.71,571.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,591.40) --
	(371.71,591.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,611.45) --
	(371.71,611.45);

@@

\path[fill=fillColor] (171.81,551.28) rectangle (185.29,566.05);

\path[fill=fillColor] (261.65,551.28) rectangle (275.13,552.81);

\path[fill=fillColor] (216.73,551.28) rectangle (230.21,552.73);

\path[fill=fillColor] (306.57,551.28) rectangle (320.05,560.59);

\path[fill=fillColor] (351.49,551.28) rectangle (364.97,552.65);

\path[fill=fillColor] ( 81.97,551.28) rectangle ( 95.45,592.68);

\path[fill=fillColor] (126.89,551.28) rectangle (140.37,561.63);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,551.28) rectangle (171.81,564.68);

\path[fill=fillColor] (248.18,551.28) rectangle (261.65,552.41);

\path[fill=fillColor] (203.26,551.28) rectangle (216.73,552.65);

\path[fill=fillColor] (293.10,551.28) rectangle (306.57,561.47);

\path[fill=fillColor] (338.02,551.28) rectangle (351.49,552.73);

\path[fill=fillColor] ( 68.50,551.28) rectangle ( 81.97,592.52);

\path[fill=fillColor] (113.42,551.28) rectangle (126.89,562.68);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,551.28) rectangle (158.34,569.17);

\path[fill=fillColor] (234.70,551.28) rectangle (248.18,553.53);

\path[fill=fillColor] (189.78,551.28) rectangle (203.26,552.97);

\path[fill=fillColor] (279.62,551.28) rectangle (293.10,558.58);

\path[fill=fillColor] (324.54,551.28) rectangle (338.02,552.41);

\path[fill=fillColor] ( 55.02,551.28) rectangle ( 68.50,593.08);

\path[fill=fillColor] ( 99.94,551.28) rectangle (113.42,559.31);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,475.68) --
	(371.71,475.68);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,495.74) --
	(371.71,495.74);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,515.80) --
	(371.71,515.80);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,535.85) --
	(371.71,535.85);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,485.71) --
	(371.71,485.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,505.77) --
	(371.71,505.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,525.82) --
	(371.71,525.82);

@@

\path[fill=fillColor] (171.81,465.65) rectangle (185.29,494.21);

\path[fill=fillColor] (254.91,465.65) rectangle (275.13,465.97);

\path[fill=fillColor] (216.73,465.65) rectangle (230.21,478.81);

\path[fill=fillColor] (306.57,465.65) rectangle (320.05,466.05);

\path[fill=fillColor] (351.49,465.65) rectangle (364.97,467.58);

\path[fill=fillColor] ( 81.97,465.65) rectangle ( 95.45,500.79);

\path[fill=fillColor] (126.89,465.65) rectangle (140.37,466.30);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,465.65) rectangle (171.81,491.41);

\path[fill=fillColor] (234.70,465.65) rectangle (254.91,466.30);

\path[fill=fillColor] (203.26,465.65) rectangle (216.73,478.97);

\path[fill=fillColor] (293.10,465.65) rectangle (306.57,466.30);

\path[fill=fillColor] (338.02,465.65) rectangle (351.49,466.62);

\path[fill=fillColor] ( 68.50,465.65) rectangle ( 81.97,503.92);

\path[fill=fillColor] (113.42,465.65) rectangle (126.89,466.38);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,465.65) rectangle (158.34,498.15);

\path[fill=fillColor] (189.78,465.65) rectangle (203.26,478.49);

\path[fill=fillColor] (279.62,465.65) rectangle (293.10,465.81);

\path[fill=fillColor] (324.54,465.65) rectangle (338.02,468.86);

\path[fill=fillColor] ( 55.02,465.65) rectangle ( 68.50,496.62);

\path[fill=fillColor] ( 99.94,465.65) rectangle (113.42,466.21);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,390.05) --
	(371.71,390.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,410.11) --
	(371.71,410.11);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,430.16) --
	(371.71,430.16);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,450.22) --
	(371.71,450.22);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,400.08) --
	(371.71,400.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,420.14) --
	(371.71,420.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,440.19) --
	(371.71,440.19);

@@

\path[fill=fillColor] (171.81,380.02) rectangle (185.29,392.06);

\path[fill=fillColor] (261.65,380.02) rectangle (275.13,380.50);

\path[fill=fillColor] (216.73,380.02) rectangle (230.21,380.90);

\path[fill=fillColor] (306.57,380.02) rectangle (320.05,406.66);

\path[fill=fillColor] (344.75,380.02) rectangle (364.97,380.34);

\path[fill=fillColor] ( 81.97,380.02) rectangle ( 95.45,398.47);

\path[fill=fillColor] (126.89,380.02) rectangle (140.37,401.44);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,380.02) rectangle (171.81,391.41);

\path[fill=fillColor] (248.18,380.02) rectangle (261.65,380.74);

\path[fill=fillColor] (203.26,380.02) rectangle (216.73,380.90);

\path[fill=fillColor] (293.10,380.02) rectangle (306.57,405.86);

\path[fill=fillColor] (324.54,380.02) rectangle (344.75,380.50);

\path[fill=fillColor] ( 68.50,380.02) rectangle ( 81.97,399.36);

\path[fill=fillColor] (113.42,380.02) rectangle (126.89,401.52);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,380.02) rectangle (158.34,393.18);

\path[fill=fillColor] (234.70,380.02) rectangle (248.18,380.18);

\path[fill=fillColor] (189.78,380.02) rectangle (203.26,380.82);

\path[fill=fillColor] (279.62,380.02) rectangle (293.10,408.10);

\path[fill=fillColor] ( 55.02,380.02) rectangle ( 68.50,396.71);

\path[fill=fillColor] ( 99.94,380.02) rectangle (113.42,401.36);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,304.42) --
	(371.71,304.42);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,324.48) --
	(371.71,324.48);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,344.53) --
	(371.71,344.53);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,364.59) --
	(371.71,364.59);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,314.45) --
	(371.71,314.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,334.51) --
	(371.71,334.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,354.56) --
	(371.71,354.56);

@@

\path[fill=fillColor] (171.81,294.39) rectangle (185.29,296.88);

@@

\path[fill=fillColor] (216.73,294.39) rectangle (230.21,295.76);

\path[fill=fillColor] (306.57,294.39) rectangle (320.05,299.04);

\path[fill=fillColor] ( 81.97,294.39) rectangle ( 95.45,366.03);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,294.39) rectangle (171.81,296.56);

@@

\path[fill=fillColor] (203.26,294.39) rectangle (216.73,295.84);

\path[fill=fillColor] (293.10,294.39) rectangle (306.57,299.69);

\path[fill=fillColor] ( 68.50,294.39) rectangle ( 81.97,365.63);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,294.39) rectangle (158.34,297.92);

\path[fill=fillColor] (189.78,294.39) rectangle (203.26,295.59);

\path[fill=fillColor] (279.62,294.39) rectangle (293.10,297.04);

\path[fill=fillColor] ( 55.02,294.39) rectangle ( 68.50,367.24);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,218.79) --
	(371.71,218.79);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,238.85) --
	(371.71,238.85);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,258.90) --
	(371.71,258.90);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,278.96) --
	(371.71,278.96);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,228.82) --
	(371.71,228.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,248.87) --
	(371.71,248.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,268.93) --
	(371.71,268.93);

@@

\path[fill=fillColor] (171.81,208.76) rectangle (185.29,222.24);

\path[fill=fillColor] (261.65,208.76) rectangle (275.13,209.96);

\path[fill=fillColor] (216.73,208.76) rectangle (230.21,213.01);

\path[fill=fillColor] (306.57,208.76) rectangle (320.05,217.26);

\path[fill=fillColor] (351.49,208.76) rectangle (364.97,210.69);

\path[fill=fillColor] ( 81.97,208.76) rectangle ( 95.45,247.27);

\path[fill=fillColor] (126.89,208.76) rectangle (140.37,224.24);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,208.76) rectangle (171.81,221.20);

\path[fill=fillColor] (248.18,208.76) rectangle (261.65,210.12);

\path[fill=fillColor] (203.26,208.76) rectangle (216.73,212.93);

\path[fill=fillColor] (293.10,208.76) rectangle (306.57,217.59);

\path[fill=fillColor] (338.02,208.76) rectangle (351.49,210.77);

\path[fill=fillColor] ( 68.50,208.76) rectangle ( 81.97,247.27);

\path[fill=fillColor] (113.42,208.76) rectangle (126.89,224.97);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,208.76) rectangle (158.34,224.00);

\path[fill=fillColor] (234.70,208.76) rectangle (248.18,209.88);

\path[fill=fillColor] (189.78,208.76) rectangle (203.26,213.17);

\path[fill=fillColor] (279.62,208.76) rectangle (293.10,216.54);

\path[fill=fillColor] (324.54,208.76) rectangle (338.02,210.61);

\path[fill=fillColor] ( 55.02,208.76) rectangle ( 68.50,247.03);

\path[fill=fillColor] ( 99.94,208.76) rectangle (113.42,223.12);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,133.16) --
	(371.71,133.16);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,153.21) --
	(371.71,153.21);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,173.27) --
	(371.71,173.27);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,193.33) --
	(371.71,193.33);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,143.19) --
	(371.71,143.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,163.24) --
	(371.71,163.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,183.30) --
	(371.71,183.30);

@@

\path[fill=fillColor] (171.81,123.13) rectangle (185.29,132.36);

\path[fill=fillColor] (216.73,123.13) rectangle (230.21,125.06);

\path[fill=fillColor] (306.57,123.13) rectangle (320.05,140.70);

@@

\path[fill=fillColor] ( 81.97,123.13) rectangle ( 95.45,150.81);

\path[fill=fillColor] (126.89,123.13) rectangle (140.37,146.96);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,123.13) rectangle (171.81,131.71);

\path[fill=fillColor] (203.26,123.13) rectangle (216.73,124.73);

\path[fill=fillColor] (293.10,123.13) rectangle (306.57,142.71);

\path[fill=fillColor] (324.54,123.13) rectangle (344.75,123.21);

\path[fill=fillColor] ( 68.50,123.13) rectangle ( 81.97,149.44);

\path[fill=fillColor] (113.42,123.13) rectangle (126.89,147.20);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,123.13) rectangle (158.34,133.00);

\path[fill=fillColor] (189.78,123.13) rectangle (203.26,125.30);

\path[fill=fillColor] (279.62,123.13) rectangle (293.10,138.61);

\path[fill=fillColor] ( 55.02,123.13) rectangle ( 68.50,152.25);

\path[fill=fillColor] ( 99.94,123.13) rectangle (113.42,146.72);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,561.31) --
	(717.20,561.31);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,581.37) --
	(717.20,581.37);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,601.43) --
	(717.20,601.43);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,621.48) --
	(717.20,621.48);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,571.34) --
	(717.20,571.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,591.40) --
	(717.20,591.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,611.45) --
	(717.20,611.45);

@@

\path[fill=fillColor] (517.31,551.28) rectangle (530.78,580.65);

\path[fill=fillColor] (607.15,551.28) rectangle (620.62,552.65);

\path[fill=fillColor] (562.23,551.28) rectangle (575.70,552.73);

\path[fill=fillColor] (696.99,551.28) rectangle (710.46,558.42);

\path[fill=fillColor] (427.47,551.28) rectangle (440.94,582.81);

\path[fill=fillColor] (472.39,551.28) rectangle (485.86,560.59);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (503.83,551.28) rectangle (517.31,580.57);

\path[fill=fillColor] (593.67,551.28) rectangle (607.15,553.37);

\path[fill=fillColor] (548.75,551.28) rectangle (562.23,552.65);

\path[fill=fillColor] (683.51,551.28) rectangle (696.99,559.47);

\path[fill=fillColor] (413.99,551.28) rectangle (427.47,580.09);

\path[fill=fillColor] (458.91,551.28) rectangle (472.39,561.79);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (490.36,551.28) rectangle (503.83,580.73);

\path[fill=fillColor] (580.19,551.28) rectangle (593.67,552.17);

\path[fill=fillColor] (535.27,551.28) rectangle (548.75,552.81);

\path[fill=fillColor] (670.03,551.28) rectangle (683.51,557.86);

\path[fill=fillColor] (400.52,551.28) rectangle (413.99,584.50);

\path[fill=fillColor] (445.44,551.28) rectangle (458.91,559.95);
\definecolor{drawColor}{gray}{0.20}

@@

\path[fill=fillColor] (517.31,465.65) rectangle (530.78,472.07);
